Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-05 manuscript/manuscript.tex
Reorganized Analytical solutions for spherical shell in manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Analytical Solutions for Spherical Shell}

The integrals that define the gravity fields in equations \ref{eq:tesseroid-pot}-\ref{eq:tesseroid-tensor} have analytical solutions for the exceptional case of a spherical shell with homogeneous density \citep{Mikuska2006,Grombein2013}.
In order to test the accuracy of their approximations, \citet{Uieda2016} and \citet{Grombein2013} compared their numerical models (tesseroids with homogeneous density) with these analytical solutions.

In case of variable density tesseroids, the comparison must obviously be made with a variable density spherical shell, whose analytical solution will depend on the chosen density function.
Because the literature has not offered it yet, we had to develop it ourselves. \todo{ no se si ponerlo asi}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Determination of distance-size and delta ratios}

In order to determine default values for the distance-size ratio ($D$)
and the delta ratio ($\delta$) that ensure both numerical accuracy and 
computation effectiveness we need to compare the numerical 
approximation with some analytical solutions.

On the homogeneous density tesseroids case, \citet{Uieda2016} and 
\citet{Grombein2013} compared their numerical model with the analytical 
solution of a spherical shell.
We could follow this idea, but for our needs the spherical shell must 
have the same density function as the numerical model, although the 
analytical solution in this case must be derived.

\subsection{Analytical Solutions for Spherical Shell}

The integrals that define the gravity fields in equations 
\ref{eq:tesseroid-pot}-\ref{eq:tesseroid-tensor} have analytical 
solutions in case of a spherical shell with homogeneous density 
\citep{Mikuska2006,Grombein2013}.
But for variable density spherical shell the problem wasn't address in 
the literature yet.
